---
title: "DCNP Colorectal trends"
author: "Dan Weinberger"
date: '2024-01-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(dplyr)
library(lubridate)
library(MASS)
library(ggplot2)
library(patchwork) # combining plots

source('./R/RunControl.R')
source('./R/OutputsControl.R')

```

## Read in Data

```{r}
a1 <- read_excel('./CONFIDENTIAL/DCNP CRC Incidence Data.xlsx') %>%
  rename(Outcome=`Incident CRC Diagnoses (N)`,
         date=Year,
         Population=`Population (N)`) %>%
  mutate( date = as.Date(date),
          monthdays = days_in_month(date)) %>%
    mutate(log_offset= log(Population/monthdays*30.3)) %>%
  arrange( date) 


```

## Panel A: Papillary <2 cm {.tabset}
```{r}
b1 <- a1 %>%
  arrange(date) %>%
  mutate(index=row_number())

set.start.date =as.Date('2020-03-01')

form1a <- ' ~ index + offset(log_offset)'
outcome <- 'Outcome_pre '
form1 <- paste0(outcome, form1a)

mod1 <- RunControl(ds=b1 ,set.start.date=set.start.date, set.form_cont1=form1)

out1 <-  OutputsControl(fitted.mod=mod1, niter=10000)
```

### RR trend
```{r}
fig1a <-out1$p.rr.trend

fig1a
```
### Obs vs expected trend
```{r}
fig2a <- out1$p.preds +ylim(0,450)
fig2a
```
### Cumulative prevented trend

```{r}
fig3a <- out1$p.cum_prevented +
  coord_cartesian( ylim=c(0,450))
fig3a
```

```{r, fig.width=4, fig.height=6}
fig2a / fig1a /fig3a +
   plot_annotation(tag_levels = 'A')
```

```{r}
plotly::ggplotly(fig1a)
```




